An Abstraction-based Approach to Network Synthesis

### 2016-10-31 paper/abstraction/paper.tex
start section 3

\newcommand{\Exit}{\KW{exit}}
\newcommand{\End}{\KW{end}}
\newcommand{\Start}{\KW{start}}
\newcommand{\Enter}{\KW{enter}}
\newcommand{\Later}{\KW{later}}
\newcommand{\Before}{\KW{before}}
\newcommand{\Internal}{\KW{internal}}
\newcommand{\Never}{\KW{never}}
\newcommand{\Only}{\KW{only}}
\newcommand{\Through}{\KW{through}}
\newcommand{\LinkKW}{\KW{link}}
\newcommand{\PathKW}{\KW{path}}
\newcommand{\Novalley}{\KW{novalley}}

@@

\subsection{Example:  The datacenter}

\begin{easylist}[itemize]
& Example of a datacenter with two peers (running BGP).
&& Each tier of the datacenter treats traffic the same
&& Since each tier will treat traffic the same, operator would like to
   avoid writing a separate configuration for each device in a given tier.
&& Operator writes 3 templates (show example of templates, including filters).

& Show example of aggregation-induced black hole
\end{easylist}

\subsection{Example:  The Backbone}

\begin{easylist}[itemize]
& Example of a backbone network with multiple peers
&& Maybe have a couple of different roles (e.g., special handling to keep traffic in the US)
&& Could show different abstractions here (e.g., one big switch)
&& Could be useful to hint at things to come, e.g., takes 2 sec to compile the abstract one
\end{easylist}

@@

\section{Propane overview}
\label{sec:propane}

\subsection{Example: The datacenter}

\begin{easylist}[itemize]
& Abstraction of datacenter tiers -- provided by a map from
  nodes in the concrete network to nodes in the abstract network.
  Also provide node and edge constraints.
&& Thus, the new topology contains only those 3 abstract nodes.
&& Rather than writting templates for each device, the operator
  writes a centralized routing policy for the network (show propane policy)

& Show generated templates from compilation (e.g., use of network-wide abstraction)

& Show example of aggregation safety checking in the abstract network --
  just give the answer + forward reference (matches with concrete example).

& Suppose now we wanted to expand this network, or configure a similar network...
\end{easylist}

\subsection{Example: The Backbone}

\begin{easylist}[itemize]
& Give the policy over the abstract network
\end{easylist}

\subsection{Language}

Placeholder for formal language definition syntax + semantics

% Examples of code given below

%\sysname lets operators configure the network with the
%abstraction that they have centralized control over routing.
%Specifically, the operator simply provides a set of high-level constraints
%that describe the
%paths traffic should---or should not---take and their relative preferences.
%\sysname specifications are written modularly via a series
%of declarations.
%For example, to begin specification of the backbone
%network from the previous section, we first express the idea that
%we prefer that traffic leave the network through \CD{R1} over \CD{R2} (to \CD{Cust}) over \CD{Peer} over \CD{Prov} (policy P1 and P3 from Figure~\ref{fig:example1}):
%%
%\begin{code}
%\Define Prefs = \Exit(R1 \Prefer R2 \Prefer Peer \Prefer Prov)
%\end{code}
%This  statement defines a set of \emph{ranked paths}, which includes
%all paths (and only those paths) for which traffic exits our network
%through either router \CD{R1}, router \CD{R2}, \CD{Peer}, or \CD{Prov}.
%The paths that exit through \CD{R1}
%are preferred (\Prefer) to those that exit through \CD{R2}, which are preferred to those that
%leave through \CD{Peer} and then \CD{Prov}.  As we
%describe in the next section, the \Exit\ expression, as well as other
%path expressions used later in this section, is simply a shorthand for
%a particular regular expression over paths that is expressible in our policy
%language. The preference operator (\Prefer) is flexible and can be used between constraints as well as among individual routers. For example, the above constraint could have been written equivalently as
%\Exit(\CD{R1}) \Prefer \ldots \Prefer ~\Exit(\CD{Prov})%

%To associate ranked paths with
%one or more prefixes, we define a \sysname \emph{policy}.
%Within a policy, statements with the form $t\;$\Path$\;p$
%associate the prefixes defined by the predicate $t$ with the set of
%ranked paths defined by the path expression $p$.  In general,
%prefix predicates can be defined by arbitrary boolean combinations
%(and, or, not) of concrete prefixes and community tags.  Here,
%we assume we have already defined the predicate \CD{PCust} for the
%customer prefixes.
%%
%In the following code, ranked paths are associated with
%customer prefixes,
%and all other prefixes (\CD{true}). Policy statements are processed in
%order with earlier policy statements taking precedence over later
%policy statements. Hence, when the predicate \True{} follows
%the statement involving \CD{PCust}, it is interpreted as
%\CD{\True{} \AND{} \NOT{}PCust}.%
%

%\begin{code}
%\Define Routing =
%    \{PCust \Path Prefs \AND \End(Cust)
%     \True  \Path Prefs \}
%\end{code}
%\noindent%

%Line 2 of this policy
%restricts traffic destined to known customer prefixes (\CD{PCust}) to only follow paths that end at the customer. In addition, it enforces the network-wide preference that traffic leaves through \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
%%
%Line 3 applies to any other traffic not matching \CD{PCust} and allows the traffic to leave through any direct neighbor with the usual preference of \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}. To summarize our progress, the \CD{Routing} policy
%implements P1, P3, and P4 from Figure~\ref{fig:example1}.%
%

%Since, routing allows transit traffic by default (\EG, traffic entering from
%\CD{Peer} and leaving through \CD{Prov}), we separately define a
%policy to enforce P2 and P5 from Figure~\ref{fig:example1}, using conjunction (\AND),
%disjunction (\OR) and negation (\NOT) of constraints.
%First, we create reusable abstractions for describing traffic that transits our network. In \sysname, this is done by creating a new parameterized definition.
%\begin{code}
%\Define transit(X,Y) = \Enter(X{\OR}Y) \AND \Exit(X{\OR}Y)
%\Define cust-transit(X,Y) = \Later(X) \AND \Later(Y)
%\end{code}
%\noindent
%Here we define transit traffic between groups of neighbors $X$ and $Y$ as traffic that enters the network through some neighbor in $X$ or $Y$ and then also leaves the network through some neighbor in either $X$ or $Y$. Similarly, we define customer transit for customer $X$ and provider $Y$ as traffic that later goes through both $X$ and $Y$ after leaving our network. Using these two new abstractions, we can now implement policies P2 and P5 with the following constraint.%

%\begin{code}
%\Define NoTrans =
%  \{\True \Path \NOT{}transit(Peer,Prov) \AND
%           \NOT{}cust-transit(Cust,Prov)\}
%\end{code}
%\noindent
%The \CD{NoTrans} constraint requires that all traffic not follow a path that transits our network between \CD{Peer} and \CD{Prov}.
%Additionally, it prevents traffic from ever following paths that leave our network and later go through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
%and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.%

%Collectively, the constraints above capture the entire policy. From them, our compiler will generate per-device import and export filters, local preferences,
%MED attributes, and community tags to ensure that the policy is
%implemented correctly under all failures.%
%

%Our datacenter example network has three main concerns:
%(1) traffic for the prefix allocated to each top-of-rack router must be able to reach that router,
%(2) local services must not leak outside the datacenter, and
%(3) aggregation must be performed on global prefixes to reduce churn
%in the network.%

%\sysname allows modular specification of each of these constraints. The first constraint is about prefix ownership---we want traffic only for certain prefixes to end up at a particular location. The following definition captures this intent.%
%

%\begin{code}
%\Define Ownership =
%    \{PG1 \Path \End(A)
%     PG2 \Path \End(B)
%     PL1 \Path \End(E)
%     PL2 \Path \End(F)
%     \True \Path \End(\Out)\}
%\end{code}
%\noindent
%This definition says that traffic for prefix \CD{PG1} is allowed to follow only paths that
%end at router \CD{A}; traffic for \CD{PG2},
%but not \CD{PG1}, must
%end at router \CD{B}; and so on.
%Any traffic destined for a prefix that is not a part of the datacenter should be allowed to leave the datacenter and end at some external location, which is otherwise unconstrained.
%The special keyword \Out{} matches any location outside the datacenter network, while the keyword \In{} will match any location inside the network.%

%For the second constraint, we define another policy:%

%\begin{code}
%\Define Locality =
%    \{PL1 \OR PL2 \Path \textbf{only}(\In)\}
%\end{code}
%\noindent
%%
%This definition says that traffic for local
%prefixes only follows paths that are internal to the network at each hop.
%This constraint guarantees that the services remain accessible only to locations
%inside the datacenter.%

%As in the backbone example, we can logically conjoin these constraints
%to specify the network-wide policy.
%However, in addition to constraints on the shape of paths,
%\sysname allows the operator to specify constraints on the BGP control plane itself.
%For instance, a constraint on aggregation is included to ensure that
%aggregation for global prefixes is performed from
%locations inside (\In) the network to locations outside (\Out).
%In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG}
%(which we assume is defined earlier)
%when advertised outside the datacenter.%

%\begin{code}
%Ownership \AND{} Locality \AND{} \Agg(PG, \In \Link \Out)
%\end{code}%

%Once \sysname compiles the policy, it is guaranteed to remain compliant under all possible failure scenarios, modulo any aggregation-induced black holes. In the presence of aggregation, the \sysname compiler will also efficiently find a lower bound on the number of failures required to create an aggregation-induced black hole.

@@

%\begin{figure*}[t]\small
%  \begin{minipage}[t]{.45\linewidth}
%  \hdr{Syntax}{}
%  \vspace*{-1\baselineskip}
%  %
%  \[ \begin{array}{rclr}
%    \hline%

%     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
%     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
%     x       &::=& d.d.d.d/d & \textit{prefix} \\
%     t       &::=& \True & \textit{true} \\
%         &\BNFALT& \NOT t & \textit{negation} \\
%         &\BNFALT& t_1 \OR{} t_2 & \textit{disjunction} \\
%         &\BNFALT& t_1 \AND{} t_2 & \textit{conjunction} \\
%         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
%         &\BNFALT& \textit{comm} = d & \textit{community test} \\
%     r       &::=& l & \textit{location} \\
%         &\BNFALT& \emptyset & \textit{empty set} \\
%         &\BNFALT& \In & \textit{internal loc} \\
%         &\BNFALT& \Out & \textit{external loc} \\
%         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
%         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
%         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
%         &\BNFALT& \NOT r & \textit{path negation} \\
%         &\BNFALT& r^* & \textit{iteration} \\
%     ln       &::=& r_1 \rightarrow r_2 & \textit{links} \\
%     cc     &::=& agg(x, ln) \BNFALT tag(d, t, ln) & \textit{control constraints} \\
%  \end{array} \]%

%  \end{minipage}
%  %
%  ~~
%  \vrule
%  ~~
%  %
%  \begin{minipage}[t]{.5\linewidth}\small
%  \hdr{Propane Expansions}{}
%  \vspace*{-1\baselineskip}
%  %
%  \[\begin{array}{rcl}
%    \hline
%    \Any           & = & \Out^* \cdot \In^+ \cdot \Out^* \\
%    \None          & = & \emptyset \\
%    \Internal      & = & \In^+ \\
%    \Only(X)       & = & \Any \cap X^* \\
%    \Never(X)      & = & \Any \cap (!X)^* \\
%    \Through(X)    & = & \Out^* \cdot \In^* \cdot X \cdot \In^* \cdot \Out^* \\
%    \Later(X)      & = & \Out^* \cdot (X \cap \Out) \cdot \Out^* \cdot \In^+ \cdot \Out^* \\
%    \Before(X)     & = & \Out^* \cdot \In^+ \cdot \Out^* \cdot (X \cap \Out) \cdot \Out^* \\
%    \End(X)        & = & \Any \cap (\Sigma^* \cdot X) \\
%    \Start(X)      & = & \Any \cap (X \cdot \Sigma^*) \\
%    \Exit(X)       & = & (\Out^* \cdot \In^* \cdot (X \cap \In) \cdot \Out \cdot \Out^*) \cup \\
%                  &        & (\Out^* \cdot \In^+ \cdot (X \cap \Out) \cdot \Out^*) \\
%    \Enter(X)      & = & (\Out^* \cdot \Out \cdot (X \cap \In) \cdot \In^* \cdot \Out^*) \cup \\
%                  &        & (\Out^* \cdot (X \cap \Out) \cdot \In^+ \cdot \Out^*) \\
%    \LinkKW(X,Y)     & = & \Any \cap (\Sigma^* \cdot X \cdot Y \cdot \Sigma^*) \\
%    \PathKW(\vec{X}) & = & \Any \cap (\Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^*) \\
%    \Novalley(\vec{X}) & = & \Any ~ \cap \\
%                  &   & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
%                  &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
%  \end{array} \]%

%  \end{minipage}%

%  \hrulefill%

%  \caption{Regular Intermediate Representation (RIR) syntax (left), and
%           Propane language expansions (right).}
%  \label{fig:rir-syntax}
%  %\vspace{-1em}
%\end{figure*}%

>>>>

\newcommand{\Exit}{\KW{exit}}
\newcommand{\End}{\KW{end}}
\newcommand{\Start}{\KW{start}}
\newcommand{\Enter}{\KW{enter}}
\newcommand{\Eventually}{\KW{eventually}}
\newcommand{\Already}{\KW{already}}
\newcommand{\Internal}{\KW{internal}}
\newcommand{\Never}{\KW{never}}
\newcommand{\Always}{\KW{always}}
\newcommand{\Through}{\KW{through}}
\newcommand{\LinkKW}{\KW{link}}
\newcommand{\PathKW}{\KW{path}}
\newcommand{\Novalley}{\KW{novalley}}

@@

@@

\section{Methane overview}
\label{sec:propane}

\sysname builds on the Propane network configuration synthesis language to let
operators specify \emph{network-wide} routing policy at a high level of abstraction.
A \sysname policy consists of a sequence of ranked constraints on the paths traffic should 
or should not take for certain IP prefix destinations.

\subsection{Concrete Methane}

Consider again the datacenter from figure~\ref{fig:example}. To configure the datacenter routing
policy, we would start by writing the following definition in \sysname:
%
\begin{code}
\Define Routing =
    \{P1 \Path \End(T1)
     P2 \Path \End(T2)
     P3 \Path \End(T3)
     P4 \Path \End(T4)
     P5 \Path \End(T5)
     P6 \Path \End(T6)
     P7 \Path \End(T7)
     P8 \Path \End(T8)
     \True \Path \Exit(Peer1 \Prefer Peer2) \}
\end{code}
\noindent%

This defines a group of constraints for basic routing behavior. The first line states 
that traffic destined for prefix $P1$ must follow a path that ends up at destination router $T1$.
A similar constraint is added for each of the prefixes P[2-8]. The final rule matches all other
prefix destinations and allows traffic to follow a path that leaves the datacenter through either
of its peers (Peer1 or Peer2) with a preference for leaving through Peer1. The \Prefer symbol indicates
that traffic should satisfy the constraint on the left whenever possible, and only resort to the backup (right)
when this is not possible due to failures.

Next we can add the locality constraint for prefixes P[5-8]. We do this by adding another group of constraints:
%
\begin{code}
\Define Locality =
    \{P5 | P6 | P7 | P8 \Path \Always(\In)\}
\end{code}
\noindent%

The Locality constraint applies to any traffic destined for a local prefix and adds
the constraint that the traffic must follow a path that matches an internal location 
(\IE, a router inside the datacenter) at each hop of the path. This prevents traffic 
from ever entering from or leaving through an external peer.

Finally, for all traffic in the datacenter, we will disallow valley routing. This constraint
can be captured with the following additions to the policy:
%
\begin{code}
\Define Tor = \{T1,T2,T3,T4,T5,T6,T7,T8\}
\Define Agg = \{A1,A2,A3,A4,A5,A6,A7,A8\}
\Define Spn = \{S1,S2\}

\Define ValleyFree =
    \{\True \Path \Novalley(Tor,Agg,Spn)\}
\end{code}
\noindent%

The first three lines define groups of routers. The top of rack (Tor) routers T[1-8], the 
aggregation routers (Agg) A[1-8], and the spine routers (Spn) S[1-2]. The next line 
adds a new constraint that applies to all traffic and ensures that traffic never follows a 
path that forms a valley between any of these three groups (\EG, going from Spn to Agg to Spn again).
As we will see in section \ryan{reference}, each of these constraints such as the valley free constraint
are really just syntactic sugar for regular expressions over topology locations.

The final policy is declared to as the conjunction of each of these constraints:
%
\begin{code}
\Define Main = 
    Routing & 
    Locality & 
    ValleyFree & 
    \Agg(PG, \In -> \Out)
\end{code}
\noindent%
The last part of the policy declares that we want to perform aggregation for global prefixes
by summarizing them into the more general prefix PG at the border of the datacenter
(\IE along any edge starting inside our datacenter and ending outside).

\subsection{Abstract Methane}

%This  statement defines a set of \emph{ranked paths}, which includes
%all paths (and only those paths) for which traffic exits our network
%through either router \CD{R1}, router \CD{R2}, \CD{Peer}, or \CD{Prov}.
%The paths that exit through \CD{R1}
%are preferred (\Prefer) to those that exit through \CD{R2}, which are preferred to those that
%leave through \CD{Peer} and then \CD{Prov}.  As we
%describe in the next section, the \Exit\ expression, as well as other
%path expressions used later in this section, is simply a shorthand for
%a particular regular expression over paths that is expressible in our policy
%language. The preference operator (\Prefer) is flexible and can be used between constraints as well as among %individual routers. For example, the above constraint could have been written equivalently as
%\Exit(\CD{R1}) \Prefer \ldots \Prefer ~\Exit(\CD{Prov})%
%To associate ranked paths with
%one or more prefixes, we define a \sysname \emph{policy}.
%Within a policy, statements with the form $t\;$\Path$\;p$
%associate the prefixes defined by the predicate $t$ with the set of
%ranked paths defined by the path expression $p$.  In general,
%prefix predicates can be defined by arbitrary boolean combinations
%(and, or, not) of concrete prefixes and community tags.  Here,
%we assume we have already defined the predicate \CD{PCust} for the
%customer prefixes.
%
%In the following code, ranked paths are associated with
%customer prefixes,
%and all other prefixes (\CD{true}). Policy statements are processed in
%order with earlier policy statements taking precedence over later
%policy statements. Hence, when the predicate \True{} follows
%the statement involving \CD{PCust}, it is interpreted as
%\CD{\True{} \AND{} \NOT{}PCust}.%

%\begin{code}
%\Define Routing =
%    \{PCust \Path Prefs \AND \End(Cust)
%     \True  \Path Prefs \}
%\end{code}
%\noindent%
%Line 2 of this policy
%restricts traffic destined to known customer prefixes (\CD{PCust}) to only follow paths that end at the customer. In addition, it enforces the network-wide preference that traffic leaves through \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
%%
%Line 3 applies to any other traffic not matching \CD{PCust} and allows the traffic to leave through any direct neighbor with the usual preference of \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}. To summarize our progress, the \CD{Routing} policy
%implements P1, P3, and P4 from Figure~\ref{fig:example1}.%%

%Since, routing allows transit traffic by default (\EG, traffic entering from
%\CD{Peer} and leaving through \CD{Prov}), we separately define a
%policy to enforce P2 and P5 from Figure~\ref{fig:example1}, using conjunction (\AND),
%disjunction (\OR) and negation (\NOT) of constraints.
%First, we create reusable abstractions for describing traffic that transits our network. In \sysname, this is done by creating a new parameterized definition.
%\begin{code}
%\Define transit(X,Y) = \Enter(X{\OR}Y) \AND \Exit(X{\OR}Y)
%\Define cust-transit(X,Y) = \Eventually(X) \AND \Eventually(Y)
%\end{code}
%\noindent
%Here we define transit traffic between groups of neighbors $X$ and $Y$ as traffic that enters the network through some neighbor in $X$ or $Y$ and then also leaves the network through some neighbor in either $X$ or $Y$. Similarly, we define customer transit for customer $X$ and provider $Y$ as traffic that later goes through both $X$ and $Y$ after leaving our network. Using these two new abstractions, we can now implement policies P2 and P5 with the following constraint.%
%\begin{code}
%\Define NoTrans =
%  \{\True \Path \NOT{}transit(Peer,Prov) \AND
%           \NOT{}cust-transit(Cust,Prov)\}
%\end{code}
%\noindent
%The \CD{NoTrans} constraint requires that all traffic not follow a path that transits our network between \CD{Peer} and \CD{Prov}.
%Additionally, it prevents traffic from ever following paths that leave our network and later go through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
%and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.%
%Collectively, the constraints above capture the entire policy. From them, our compiler will generate per-device import and export filters, local preferences,
%MED attributes, and community tags to ensure that the policy is
%implemented correctly under all failures.%%

%Our datacenter example network has three main concerns:
%(1) traffic for the prefix allocated to each top-of-rack router must be able to reach that router,
%(2) local services must not leak outside the datacenter, and
%(3) aggregation must be performed on global prefixes to reduce churn
%in the network.%
%\sysname allows modular specification of each of these constraints. The first constraint is about prefix ownership---we want traffic only for certain prefixes to end up at a particular location. The following definition captures this intent.%%

%\begin{code}
%\Define Ownership =
%    \{PG1 \Path \End(A)
%     PG2 \Path \End(B)
%     PL1 \Path \End(E)
%     PL2 \Path \End(F)
%     \True \Path \End(\Out)\}
%\end{code}
%\noindent
%This definition says that traffic for prefix \CD{PG1} is allowed to follow only paths that
%end at router \CD{A}; traffic for \CD{PG2},
%but not \CD{PG1}, must
%end at router \CD{B}; and so on.
%Any traffic destined for a prefix that is not a part of the datacenter should be allowed to leave the datacenter and end at some external location, which is otherwise unconstrained.
%The special keyword \Out{} matches any location outside the datacenter network, while the keyword \In{} will match any location inside the network.%
%For the second constraint, we define another policy:%
%\begin{code}
%\Define Locality =
%    \{PL1 \OR PL2 \Path \textbf{only}(\In)\}
%\end{code}
%\noindent
%%
%This definition says that traffic for local
%prefixes only follows paths that are internal to the network at each hop.
%This constraint guarantees that the services remain accessible only to locations
%inside the datacenter.%
%As in the backbone example, we can logically conjoin these constraints
%to specify the network-wide policy.
%However, in addition to constraints on the shape of paths,
%\sysname allows the operator to specify constraints on the BGP control plane itself.
%For instance, a constraint on aggregation is included to ensure that
%aggregation for global prefixes is performed from
%locations inside (\In) the network to locations outside (\Out).
%In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG}
%(which we assume is defined earlier)
%when advertised outside the datacenter.%
%\begin{code}
%Ownership \AND{} Locality \AND{} \Agg(PG, \In \Link \Out)
%\end{code}%
%Once \sysname compiles the policy, it is guaranteed to remain compliant under all possible failure scenarios, modulo any aggregation-induced black holes. In the presence of aggregation, the \sysname compiler will also efficiently find a lower bound on the number of failures required to create an aggregation-induced black hole.

@@

\begin{figure*}[t]\small
  \begin{minipage}[t]{.45\linewidth}
  \hdr{Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
    \hline%

     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
     x       &::=& d.d.d.d/d & \textit{prefix} \\
     t       &::=& \True & \textit{true} \\
         &\BNFALT& \neg t & \textit{negation} \\
         &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
         &\BNFALT& t_1 \wedge t_2 & \textit{conjunction} \\
         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
     r       &::=& l & \textit{location} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT r & \textit{path negation} \\
         &\BNFALT& r^* & \textit{iteration} \\
     cc     &::=& agg(x, r_1 \rightarrow r_2)  & \textit{control constraints} \\
  \end{array} \]%

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}\small
  \hdr{Propane Expansions}{}
  \vspace*{-1\baselineskip}
  %
  \[\begin{array}{rcl}
    \hline
    \Any               & = & \Sigma^* \\
    \None              & = & \emptyset \\
    \Internal          & = & \In^+ \\
    \Always(X)         & = & X^* \\
    \Never(X)          & = & (!X)^* \\
    \Through(X)        & = & \Sigma^* \cdot X \cdot \Sigma^* \\
    \Eventually(X)     & = & \Out^* \cdot (X \cap \Out) \cdot \Out^* \cdot \In^+ \cdot \Out^* \\
    \Already(X)        & = & \Out^* \cdot \In^+ \cdot \Out^* \cdot (X \cap \Out) \cdot \Out^* \\
    \End(X)            & = & \Sigma^* \cdot X \\
    \Start(X)          & = & X \cdot \Sigma^* \\
    \Enter(X)          & = & \Sigma^* \cdot \Out \cdot (X \cap \In) \cdot \Sigma^* ~ \cup \\
                       &   & \Sigma^* \cdot (X \cap \Out) \cdot \In \cdot \Sigma^* \\
    \Exit(X)           & = & \Sigma^* \cdot \In \cdot (X \cap \Out) \cdot \Sigma^* ~ \cup \\
                       &   & \Sigma^* \cdot (X \cap \In) \cdot \Out \cdot \Sigma^* \\
    \LinkKW(X,Y)       & = & \Sigma^* \cdot X \cdot Y \cdot \Sigma^* \\
    \PathKW(\vec{X})   & = & \Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^* \\
    \Novalley(\vec{X}) & = & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
                       &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
  \end{array} \]%

  \end{minipage}%

  \hrulefill%

  \caption{Regular Intermediate Representation (RIR) syntax (left), and
           Propane language expansions (right).}
  \label{fig:rir-syntax}
  %\vspace{-1em}
\end{figure*}%
